Manuscript

### 2017-06-26 manuscript.Rmd
Switched Denver data source from GDB to geojson files

## Introduction

This research will identify the correlation between size and access to urban parks, and physical activity, obesity and mental health at the neighborhood level. Proximity to parks is associated with increased physical activity and reduced obesity, but little research has been conducted on the relationship between accessibility to parks and health outcomes.

@@

##
Our anticipated results will assess the difference in physical activity and obesity at the neighborhood level when comparing proximity to parks and access to parks of various sizes and qualities as defined by park choice accessibility. We hope to make progress in achieving the Healthy People 2020 goals on physical activity, reduced sedentary behavior, and building healthy communities.

@@

# Methods

```{r load_data}
denver_tracts <- geojson_read("data/denver_tracts.geojson", what = "sp")
denver_parks <- geojson_read ("data/denver_parks.geojson", what = "sp")

@@

>>>>

## Introduction
This research will identify the correlation between size and access to urban parks, and physical activity, obesity and mental health at the neighborhood level. Proximity to parks is associated with increased physical activity and reduced obesity, but little research has been conducted on the relationship between accessibility to parks and health outcomes.

@@

## Results
Our anticipated results will assess the difference in physical activity and obesity at the neighborhood level when comparing proximity to parks and access to parks of various sizes and qualities as defined by park choice accessibility. We hope to make progress in achieving the Healthy People 2020 goals on physical activity, reduced sedentary behavior, and building healthy communities.

@@

# Methods
```{r load_data}
denver_tracts <- geojson_read("data/denver_tracts.geojson", what = "sp")
denver_parks <- geojson_read ("data/denver_parks.geojson", what = "sp")

@@

## Denver

Load Denver geospatial data (tracts and parks):
```{r denver_data}

#tracts <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_Final") 
plot(denver_tracts)

#parks <- readOGR(dsn = "data/Denver_Data.gdb", layer = "Denver_All_Parks") 
plot(denver_parks)
```

Transform the attribute table into a tibble and select the relevant variables:
```{r show_denverdata}
denver_tracts@data <- tbl_df(tracts@data) %>%
  select(GEOID_TRAC, OBESITY, Park_Percent, PhysAct, MENTAL, Income1, Income2, Income3, Income4, Income5, Income6, Income7, Income8, Income9, Income10, Pop_Density, FulltimeWork, CollegePercent, Pct0to17, Pct18to29, Pct30to64, Pct65plus, SinglePercent, PctWhite, PctBlack, PctNative, PctAsian, PctPacific, PctOther, PctHispanic) %>%
    mutate_each(funs(ifelse(is.na(.), 0, .)), Park_Percent)
tracts@data
```

Calculate the logsum given the tracts and parks dataset:
```{r denver_accessibility}
source('R/size00001dist5.R', echo=TRUE)
denver_tracts$park_ls <- calculate_park_logsums(denver_tracts, denver_parks, betas = c(.00001, -5))
```

Create regression equations for use in spatial econometric models:
```{r denver_equations}
denver_base_formula <- formula(~Income1 + Income2 + Income3 + Income4 + Income5 + Income6 + Income7 + Income8 + Income9 + Income10 + log(Pop_Density) + FulltimeWork + CollegePercent + SinglePercent + Pct0to17 + Pct18to29 + Pct30to64 + Pct65plus + PctWhite + PctBlack + PctNative + PctAsian + PctPacific + PctOther + PctHispanic)

denver_parks_formula <- update(base_formula, . ~ . + park_ls)
```

Locate the centroid of all parks and all census tracts and create a distance matrix:
```{r denver_distancematrix}
tract_centroids <- gCentroid(denver_tracts, byid = TRUE) #if byid = FALSE, then centroid of "all" points
park_centroids <- gCentroid(denver_parks, byid = TRUE)
distance_matrix <- gDistance(tract_centroids, park_centroids, byid = TRUE)
dim(distance_matrix)
```

Create a spatial weights matrix:
```{r denver_W}
neighbors <- poly2nb(denver_tracts, queen = FALSE)
W <- nb2listw(neighbours = neighbors, zero.policy = TRUE)
print(W, zero.policy = TRUE)
```

Estimate spatial econometric models for the `OBESITY` variable. The first model of each different type does not include `park_ls`:
```{r denver_spmodels_obesity}
denver_obese_sem <- errorsarlm(update(denver_base_formula, OBESITY ~ .), data = denver_tracts@data, 
                      listw = W, zero.policy = TRUE)
denver_obese_sem2 <- errorsarlm(update(denver_parks_formula, OBESITY ~ .), data = denver_tracts@data, 
                      listw = W, zero.policy = TRUE)
denver_obese_sdm <- lagsarlm(update(denver_base_formula, OBESITY ~ .), data = denver_tracts@data, 
                      listw = W, zero.policy = TRUE, type = "mixed")
denver_obese_sdm2 <- lagsarlm(update(denver_parks_formula, OBESITY ~ .), data = denver_tracts@data, 
                      listw = W, zero.policy = TRUE, type = "mixed")
```

Estimate spatial econometric models for the `PhysAct` variable. The first model of each different type does not include `park_ls`:
```{r denver_spmodels_physact}
denver_physact_sem <- errorsarlm(update(denver_base_formula, PhysAct ~ .), data = denver_tracts@data, 
                          listw = W, zero.policy = TRUE)
denver_physact_sem2 <- errorsarlm(update(denver_parks_formula, PhysAct ~ .), 
                           data = denver_tracts@data, listw = W, zero.policy = TRUE)
denver_physact_sdm <- lagsarlm(update(denver_base_formula, PhysAct ~ .), data = denver_tracts@data, 
                        listw = W, zero.policy = TRUE, type = "mixed")
denver_physact_sdm2 <- lagsarlm(update(denver_parks_formula, PhysAct ~ .), data = denver_tracts@data,
                         listw = W, zero.policy = TRUE, type = "mixed")
```

Estimate spatial econometric models for the `MENTAL` variable. The first model of each different type does not include `park_ls`:
```{r denver_spmodels_mental}
denver_mental_sem <- errorsarlm(update(denver_base_formula, MENTAL ~ .), data = denver_tracts@data, 
                          listw = W, zero.policy = TRUE)
denver_mental_sem2 <- errorsarlm(update(denver_parks_formula, MENTAL ~ .), 
                           data = denver_tracts@data, listw = W, zero.policy = TRUE)
denver_mental_sdm <- lagsarlm(update(denver_base_formula, MENTAL ~ .), data = denver_tracts@data, 
                        listw = W, zero.policy = TRUE, type = "mixed")
denver_mental_sdm2 <- lagsarlm(update(denver_parks_formula, MENTAL ~ .), data = denver_tracts@data,
                         listw = W, zero.policy = TRUE, type = "mixed")
```

Calculate the impacts of the spatial durbin models:
```{r denverSDM_impacts}
listw <- as(W, "CsparseMatrix")
tr_mult <- trW(listw, type="mult")
tr_MC <- trW(listw, type="MC")
set.seed(1)

denver_noparks_obesemult <- impacts(denver_obese_sdm, tr=tr_mult)
denver_parks_obesemult <- impacts(denver_obese_sdm2, tr=tr_mult)
denver_noparks_obeseMC <- impacts(denver_obese_sdm, tr=tr_MC)
denver_parks_obeseMC <- impacts(denver_obese_sdm2, tr=tr_MC)

denver_noparks_physactmult <- impacts(denver_physact_sdm, tr=tr_mult)
denver_parks_physactmult <- impacts(denver_physact_sdm2, tr=tr_mult)
denver_noparks_physactMC <- impacts(denver_physact_sdm, tr=tr_MC)
denver_parks_physactMC <- impacts(denver_physact_sdm2, tr=tr_MC)

denver_noparks_mentalmult <- impacts(denver_mental_sdm, tr=tr_mult)
denver_parks_mentalmult <- impacts(denver_mental_sdm2, tr=tr_mult)
denver_noparks_mentalMC <- impacts(denver_mental_sdm, tr=tr_MC)
denver_parks_mentalMC <- impacts(denver_mental_sdm2, tr=tr_MC)
```

Compare the models with `htmlreg()`. First the obesity models:
```{r denver_obesity_summary, results="asis", eval=FALSE}
denver_obesity_models <- list(denver_obese_sem, denver_obese_sem2, denver_obese_sdm, denver_obese_sdm2)
names(denver_obesity_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
                                rep(c("Base", "Parks")))
htmlreg(denver_obesity_models, caption = "Denver: Models of Obesity Prevalence")
```

Next, the physical activity models:
```{r denver_physact_summary, results="asis", eval=FALSE}
denver_physact_models <- list(denver_physact_sem, denver_physact_sem2, denver_physact_sdm, denver_physact_sdm2)
names(denver_physact_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
                                rep(c("Base", "Parks")))
htmlreg(denver_physact_models, caption = "Denver: Models of Physical Activity Participation")
```

And third, the mental health models:
```{r denver_mental_summary, results="asis", eval=FALSE}
denver_mental_models <- list(denver_mental_sem, denver_mental_sem2, denver_mental_sdm, denver_mental_sdm2)
names(denver_mental_models) <-  paste(rep(c("SEM", "SDM"), each = 2),
                                rep(c("Base", "Parks")))
htmlreg(denver_physact_models, caption = "Denver: Models of Variation in Self-Reported Mental Health")
```

## Boston
```{r boston_models}

```

```{r bostonSDM_impacts}

```

##New York City
```{r nyc_models}

```

```{r nycSDM_impacts}

```
